Language-Based Security for Low-Level MPC

### 2024-05-22 ppdp24/intro.tex
checkpoint

Our work provides a complete methodology for end-to-end verification
of MPC protocols via three components:
%
\begin{enumerate}
\item A \textbf{low-level language} for defining MPC primitives
  (\S\ref{section-lang}).
\item A \textbf{fully-automated verification method} for low-level MPC
  primitives in $\mathbb{F}_2$ (\S\ref{section-bruteforce}).
\item A \textbf{partially-automated verification method} for
  high-level MPC protocols, which leverages automated proofs for
  low-level primitives (\S\ref{section-example-gmw}).
\end{enumerate}
%
As part of this methodology, we also develop hyperproperties that
encode MPC security that may be of independent interest. The complete
methodology enables the verification of real-world MPC protocols like
GMW~\cite{goldreich2019play}.

>>>>

In summary, our work provides a complete methodology for end-to-end verification
of MPC protocols via three components:
%
\begin{enumerate}
\item A \textbf{low-level language} for defining MPC primitives
  (Section \ref{section-lang}) with an associated metalanguage
  to ease programming (Section \ref{section-metalang}).
\item A \textbf{fully-automated verification method} for low-level MPC
  primitives in $\mathbb{F}_2$ (Section \ref{section-bruteforce}).
\item A \textbf{partially-automated verification method} for
  MPC protocols, which leverages automated proofs for
  low-level primitives (Section \ref{section-example-gmw}).
\end{enumerate}
%
As part of this methodology, we also develop hyperproperties that
encode MPC security that may be of independent interest. The complete
methodology enables the verification of real-world MPC protocols like
GMW~\cite{goldreich2019play}.
